%------------------------------------------------------------------------------
% Resume Template (Parameterized)
% Source derived from original cv.tex
% Placeholders use double curly braces {{PLACEHOLDER}} to be filled by pipeline.
% Sections with repeating content use BLOCK markers:
%   % BEGIN_<BLOCK_NAME>
%   {{BLOCK_NAME}}
%   % END_<BLOCK_NAME>
%------------------------------------------------------------------------------

\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{soul}
\input{glyphtounicode}
\usepackage[margin=0.5in]{geometry}
\usepackage[default]{sourcesanspro}

% Subtle gray for footer attribution (watermark-like)
\definecolor{footergray}{gray}{0.70}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
% Footer note (single-page) showing generator attribution (right aligned, muted gray)
\fancyfoot[R]{\scriptsize\textcolor{footergray}{Auto-generated via \href{https://github.com/koshikg/resume-ai-accelerator}{resume-ai-accelerator}}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% (Removed explicit titleformat for \section; we'll use custom \ResumeSection macro instead)
\pdfgentounicode=1
\definecolor{lightyellow}{cmyk}{0.00, 0.05, 0.20, 0.00}
\sethlcolor{lightyellow}

%--------------- Custom commands & typography -----------------------
% Compact spacing ONLY used in Experience via these macros
% Experience-specific compact list macros (to keep other sections unaffected)
\newcommand{\expItem}[1]{\item{{#1 \vspace{-4pt}}}}
\newcommand{\expItemListStart}{\begin{itemize}}
\newcommand{\expItemListEnd}{\end{itemize}\vspace{-4pt}}
\newcommand{\expProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}#1 & \textit{ #2} \\ \end{tabular*}\vspace{-6pt}}
\newcommand{\sectionspace}{\vspace{-20pt}}
\newcommand{\subheadingtitlevspace}{\vspace{-3pt}}
\newcommand{\resumeItem}[1]{\item{{#1 \vspace{-4pt}}}} % bullet tightness
\newcommand{\titleItem}[1]{\textbf{#1}}
\newcommand{\highlight}[1]{\textsl{\textbf{#1}}}
\newcommand{\resumeSubheading}[4]{\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}l@{}l}{#1} & \titleItem{#3} | {#2} & \textit{#4}\\\end{tabular*}\vspace{-8pt}}
\newcommand{\resumeSubSubheading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\textit{#1} & \textit{#2} \\\end{tabular*}\vspace{-2pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}#1 & \textit{ #2} \\\end{tabular*}\vspace{-6pt}}
\newcommand{\resumeSubHeadingListStart}{\subheadingtitlevspace\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

% Name & Section styling macros (consistent typography)
\newcommand{\ResumeName}[1]{\textbf{\fontsize{18pt}{20pt}\selectfont #1}}
% Section heading macro
\newcommand{\ResumeSection}[1]{\par{\fontsize{11pt}{13pt}\selectfont \MakeUppercase{#1}}\vspace{1pt}\hrule height 0.6pt}
% Unified gap after each section content (tweak here for global spacing)
% No extra gap after section content (can be re-enabled if needed)
\newcommand{\SectionContentGap}{}

% Reduce itemize left margin globally for compactness (override default if desired)
\setlist[itemize]{leftmargin=0.15in}

\begin{document}

% -------------------------------------
% HEADER (Parameterized)
% -------------------------------------
\begin{flushleft}
    \ResumeName{Kaushik Gayal} \\
    \textit{Melbourne, VIC, Australia} $|$ 
    \textit{+61 0431 989 030} $|$  
    \href{mailto:gayal.kaushik@gmail.com}{\textit{gayal.kaushik@gmail.com}} $|$
    \href{https://kaushik.gayal.dev}{\textit{https://kaushik.gayal.dev}} $|$
    \href{https://www.linkedin.com/in/kaushik-gayal-02a57316/}{\textit{@linkedin}} $|$
    \href{https://github.com/koshikg}{\textit{@github}}
    \vspace{-2pt}
\end{flushleft}

% -------------------------------------
% PROFESSIONAL SUMMARY
% -------------------------------------
\ResumeSection{Professional Summary}
\vspace{-2pt}
\begin{itemize}[leftmargin=0.15in, label={}]
    % BEGIN_PROFESSIONAL_SUMMARY
    \item{Technologist with 15+ years across cloud, DevOps, and application engineering guiding ideation, design, build, and deployment. Recognized for ownership, curiosity, and delivering modern Azure platform solutions, infrastructure automation, and secure, observable systems.}
    % END_PROFESSIONAL_SUMMARY
\end{itemize}


% -------------------------------------
% CERTIFICATIONS
% -------------------------------------
\ResumeSection{Certifications}\vspace{-8pt}
% Two-column compact list
\begin{multicols}{2}
\begin{itemize}[leftmargin=0.1in, itemsep=0pt, parsep=0pt, topsep=0pt]
% BEGIN_CERTIFICATIONS
\item {Certified Kubernetes Administrator}
\item {AZ-305 Designing Microsoft Azure Infrastructure Solutions}
\item {AZ-500 Microsoft Azure Security Technologies}
\item {Microsoft Certified DevOps Engineer Expert}
\item {ICP: IC Agile Certified Professional}
\item {NIDA Corporate Presentation Skills}
% END_CERTIFICATIONS
\end{itemize}
\end{multicols}


% -------------------------------------
% TECHNICAL SKILLS
% -------------------------------------
\ResumeSection{Technical Skills}\vspace{2pt}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=1pt, topsep=0pt, parsep=0pt]
% BEGIN_TECHNICAL_SKILLS
  \item{\textbf{CLOUD:} Azure AI Foundry, Azure Container Apps and Jobs, Azure Container Instances, Azure Container Registry, App Gateway, Load balancer, Traffic Manager, VNets, Private DNS Zones, Azure Resolver, Sentinel, VMSS, VMs, Bastian, Azure Firewall, RBAC, Functions, Durable Functions, App Service, Service Bus, Azure Blobs, Tables, Queues, File Share, Azure AD, Cosmos DB, Key Vault, Logic Apps, SQL Servers, Dashboards, Application Insights, Log Analytics Workspace, Entra, Azure AD B2C}
  \item{\textbf{LANGUAGES AND FRAMEWORKS:} C\#, Python, PowerShell, Bash, SQL, ASP.NET, .NET Core, Entity Framework, Angular, Bootstrap, React}
  \item{\textbf{DEVSECOPS AND IAC:} Azure DevOps, GitHub, GitLab, Jenkins, Octopus Deploy, Ansible, Terraform, Bicep, ARM, Pulumi, SonarCloud, Snyk, CodeQL, Fortify, Whitesource, Prisma Cloud, Checkov}
  \item{\textbf{OBSERVABILITY:} Prometheus, Datadog, Dynatrace, AppDynamics, Grafana}
  \item{\textbf{TESTING FRAMEWORKS:} xUnit, Pester, TerraTest, Ranorex, Selenium, Playwright}
  \item{\textbf{REPORTING and AUTOMATION:} Power BI, PowerApps, Logic Apps, Autosys, Azure Automation, Powershell}
% END_TECHNICAL_SKILLS
\end{itemize}

% -------------------------------------
% EXPERIENCE
% -------------------------------------
\ResumeSection{Experience}\vspace{2pt}
\resumeSubHeadingListStart
% BEGIN_EXPERIENCE
\expProjectHeading{\titleItem{Senior DevOps Consultant} $|$ \emph{Endava - RioTinto}}{Nov 2023 -- Present}
\expItemListStart
\expItem{DevSecOps implentation and process improvements across 8 different projects, implementing shift-left security scanning, automated compliance, testing, standardizing delivery pipelines, branching and observability.}
\expItem{Consulted and implemented zero trust architecture as a template for internal projects.}
\expItem{Modern CD implementation using LaunchDarkly, ArgoCD, HELM.}
\expItem{Ranorex UI testing implemention for windows applications.}
\expItem{Implemented Agentic DevOps leveraging GitHub for source code and ADO for existing boards and pipelines for a windows application project.}
\expItem{Consulting client for scalable implemention of DevSecOps using Internal Developer Platforms and creation of shared Terraform modules.}
\expItem{Migrated build pipelines from TeamCity and deploy pipelines from Octopus Deploy to Azure DevOps for a big legacy complex project generating highest revenue for RioTinto.}
\expItem{Implemented templates for Managed DevOps Pools which will be consumed by whole org on a self service basis.}
\expItem{On prem Docker Swarm implementation for a modernization of a legacy project with server configs using Ansible.}
\expItem{Standardising notifications using Azure Functions, Logic Apps and Teams Notifications using Adaptive Cards.}
\expItem{Knowledge sharing, mentoring, documentation to improve the learning culture in the org.}
\expItemListEnd
\expProjectHeading{\titleItem{Senior Consultant} $|$ \emph{Contino (Cognizant Servian) - BHP}}{Mar 2022 -- Nov 2023}
\expItemListStart
\expItem{Led internal Squad 0 improvements and best practice adoption.}
\expItem{Directed 7-engineer team delivering platform and customer enhancements.}
\expItem{Planned and delivered Azure Landing Zone using CAF Terraform modules.}
\expItem{Executed license migration project saving \textasciitilde{}\$130K.}
\expItem{Automated large-scale GitLab SaaS repo migration with Python.}
\expItemListEnd
\expProjectHeading{\titleItem{Senior DevOps Engineer} $|$ \emph{Guild Group}}{Feb 2020 -- Mar 2022}
\expItemListStart
\expItem{Established DevOps processes and CI/CD automation with Terraform \& Azure DevOps.}
\expItem{Automated Guidewire environment provisioning and DR infrastructure.}
\expItem{Implemented observability with Datadog + App Insights; integrated alerting.}
\expItem{Drove infrastructure automation for production and DR workloads.}
\expItem{Built dashboards and agile workflows (Azure Boards \& JIRA).}
\expItemListEnd
\expProjectHeading{\titleItem{Azure Developer} $|$ \emph{Guild Group}}{Aug 2018 -- Feb 2020}
\expItemListStart
\expItem{Developed and maintained SuperSuper microservices (Functions, App Services, Service Bus, Storage, Cosmos DB, B2C).}
\expItem{Implemented cost optimization and security hardening across subscriptions.}
\expItem{Created admin tooling (ASP.NET MVC) and automation with Logic Apps/Teams.}
\expItemListEnd
% END_EXPERIENCE
\resumeSubHeadingListEnd

% -------------------------------------
% EARLIER ROLES
% -------------------------------------
\ResumeSection{Earlier Roles}\vspace{-2pt}
\begin{itemize}[leftmargin=0.15in, label={}]
% BEGIN_EARLIER_ROLES
\item{\titleItem{Wells Fargo (2012--2018)}{: Senior Technology Specialist; Technology Specialist; Senior Analyst} \\[-2pt]
        \titleItem{Wipro Limited (2010--2012)}{: Software Engineer; Engineer Trainee}}
% END_EARLIER_ROLES
\end{itemize}

% -------------------------------------
% EDUCATION
% -------------------------------------
\ResumeSection{Education}\vspace{-2pt}
\resumeSubHeadingListStart
% BEGIN_EDUCATION
\resumeProjectHeading{\titleItem{Birla Institute of Applied Sciences | B.Tech Computer Science \& Engineering (Honours) | 2006--2010}}{}
% END_EDUCATION
\resumeSubHeadingListEnd

\end{document}
